Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-05-04 mu/article/article.tex
Ading arrows to V^{ab} rtp plots.
Including fixing spin plots.

% preamble:

@@

\subsection{Pure spin velocity} % (fold)
\label{sec:theory-pure_spin_current}

@@

Now we define the spin velocity, $\mathcal{V}^{\mathrm{ab}}$ as the speed at
which the spin polarized in the $\mathrm{b}$   direction moves along the
$\mathrm{a}$ direction when a normal incident beam reaches the $xy$ plane with a
polarization angle $\alpha$. Then,
\begin{widetext}
\begin{align}
\mathcal{V}^{\mathrm{ab}} (\omega) 
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha) + 
2\mu^{\mathrm{abxy}}(\omega)
E^{2}(\omega)\cos(\alpha)\sin(\alpha)}
{\xi^{\mathrm{xx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha)},
\nonumber \\
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)\sin^{2}(\alpha) + 
\mu^{\mathrm{abxy}}(\omega)\sin(2\alpha)}
{\xi^{\mathrm{xx}}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)}.
\label{eq:vab}
\end{align}
\end{widetext}

@@

\subsection{Layer-by-layer analysis.}\label{sec:theory-layer}

@@

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% Res: mu & V^{ab} comparison %%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{plots/vab-str-comp}
    \caption{Comparison of most intense responses for
    $\mathcal{V}^{\mathrm{ab}}$ for \emph{alt}, \emph{up}, CdSe, and GaAs
    structures}
    \label{fig:vab-str-comp}
\end{figure}

In figure \ref{fig:vab-str-comp} we present a comparison of the most intense
responses resulting from evaluate the Eq. \eqref{eq:vab} for the \emph{alt} and
\emph{up} 2D structures vs. CdSe and GaAs bulk structures. As we can see from
this figure the most intense response corresponds to the \emph{up} structure
centered at 0.088\,eV corresponding to the terahertz radiation and reaching a
spin velocity of 87.16\,Km/s.
% 
In the other hand, for an energy range from 0.66\,eV to 3.0\,eV all the
four structures have contributions in the same order of magnitude. 
% 
Starting with the 2D structures we have that the \emph{up} structure has other
two peaks centered at 1.94\,eV and 1.97\,eV reaching spin velocities of
22.2\,Km/s and -29.7\,Km/s, respectively, and the \emph{alt} structure has two
peaks centered at 0.72\,eV and 0.91\,eV reaching spin velocities of -40.2\,Km/s
and -32.9\,Km/s, respectively.
% 
Then, for the bulk structures we have that the CdSe has only one intense
response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
GaAs structure has a large and almost planar zone where the response is hold
reaching the maximum for an incoming beam of energy of 2.31\,eV and reaching a
spin velocity of -21.6\,Km/s.
% 
In table \ref{tab:vab-str-comp} we present the comparison of this values for the 2D and bulk structures.
% 
\begin{table}[t]
\begin{tabular}{cccccc}
\hline
\hline
Kind of  & 
\multirow{2}{*}{\quad Structure \quad} & 
Pol. &
Energy & 
\multicolumn{2}{c}{$\mathcal{V}^{\mathrm{ab}}(\omega)$}\\
\cline{5-6}
system & & Ang. & [eV] & $\mathrm{ab}$ \quad & [Km/s]\\
\hline
\hline
2D   & \emph{up}    & 40    & 0.09  & $\mathrm{yz}$ &  87.16    \\
     &              &       & 1.94  & $\mathrm{yz}$ &  22.22    \\
     &              &       & 1.97  & $\mathrm{yz}$ & -29.70    \\
\hline
2D   & \emph{alt}   & 145   & 0.72  & $\mathrm{yz}$ & -40.21    \\
     &              &       & 0.91  & $\mathrm{yz}$ & -32.89    \\
\hline
bulk &  CdSe        & 90    & 0.91  & $\mathrm{zz}$ & -26.87    \\
\hline
bulk &  GaAs        & 90    & 2.31  & $\mathrm{xx}$ & -21.62    \\
\hline
\hline
\end{tabular}
\caption{Comparison of the reported maxima values of $\mathcal{V}^{\mathrm{ab}}$
for different structures and the corresponding polarization angle $\alpha$ and
energy values.}
\label{tab:vab-str-comp}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%% Results: Fixing spin %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\blindtext
\blindtext

@@

% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V^{a}| 3D
% %% files: 
% %% magv.sm_0.03_xb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% magv.sm_0.03_yb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% up-3d-vab.gp
% %%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vx-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{up} structure 
    \label{fig:up-3d-vy-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
    structure. The maximum response zone is localized for an energy range from
    0.04\,eV to 0.12\,eV and for a polarization angle of the
    incoming beam from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-3d-1}
\end{figure}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}
    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
    \emph{up} structure. Both maxima where obtained for a polarization
    angle $\alpha=40^{\circ}$. }
    \label{fig:up-vab-comp-rtp-1}
\end{figure}

For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
0.16\,eV where we found the most intense response for $\mathcal{V}^{\mathrm{x}}$
and $|\mathcal{V}^{\mathrm{y}}|$. In Fig. \ref{fig:up-3d-1} we present the
$\mathcal{V}^{\mathrm{a}}$ spectra resulting from evaluate again Eq. 
\eqref{eq:vv-mag} using different polarization angles $\alpha$ in Eq.  
\eqref{eq:vab} but now for the C$_{16}$H$_{8}$-up structure. We can see that the
onset of the response is when the energy of the incoming light is the same of
the gap energy.
% 
From this picture we can see that for the zone between the energy range of
0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
$45^{\circ}$ is the zone where the maximum zone of response for both,
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ is hold.
% 
We found that the absolute maximum of the response is obtained when the
polarization angle is $\alpha=40^{\circ}$ and the energy of the incoming beam is
0.088\,eV.
%
In the top frames of  Figs. \ref{fig:up-vx-comp-rtp-1} and 
% 
\ref{fig:up-vy-comp-rtp-1} we present the results of
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ (left scale)
fixing the polarization angle to $\alpha=40^{\circ}$ for the \emph{up} structure
vs photon energy and the corresponding polar $\varphi$ and azimuthal $\theta$
angles (right scale). In the bottom frames of same figures we present the decomposition of
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ in the
corresponding $\mathcal{V}^{\mathrm{xx}}$, 
$\mathcal{V}^{\mathrm{xy}}$,
$\mathcal{V}^{\mathrm{xz}}$, and
$\mathcal{V}^{\mathrm{yx}}$, 
$\mathcal{V}^{\mathrm{yy}}$,
$\mathcal{V}^{\mathrm{yz}}$ 
components with $\alpha$ fixed to $40^{\circ}$. 
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vx-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{up} structure 
    \label{fig:up-3d-vy-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$
    response for C$_{16}$H$_{8}$-up structure. The local maxima responses zones
    are localized for an energy range from 1.95\,eV to 2.00\,eV and for
    polarization angles of the incoming beam from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-3d-2}
\end{figure}

@@

1.80\,eV to 2.10\,eV presented in Fig. \ref{fig:up-3d-2} where two local maxima

@@

\textbf{Alt structure.}
% %%%%%%%%%%%%%%%%%
% %% Description of ALT |V^{a}| 3D
% %% files: 
% %% magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
% %% magv.sm_0.03_yb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
% %% alt-3d-vab.gp
% %%%%%%%%%%%%%%%%%
\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vx}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vxb}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vy}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vyb}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$
    responses for C$_{16}$H$_{8}$-alt structure. The maxima responses zones are
    localized for an energy range from 0.90\,eV to 0.93\,eV and for polarization
    angles of the incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
    \label{fig:alt-3d}
\end{figure}

@@

\ref{fig:alt-3d} we present the $|\mathcal{V}^{\mathrm{a}}|$ spectra resulting 

>>>>

@@

{\color{red}
\subsection{Pure spin velocity} % (fold)
\label{sec:theory-pure_spin_current}

@@

Now we define the spin velocity, $\mathcal{V}^{\mathrm{ab}}$ as the speed at
which the spin polarized in the $\mathrm{b}$   direction moves along the
$\mathrm{a}$ direction when a normal incident beam reaches the $xy$ plane with a
polarization angle $\alpha$. Then,
} % COLOR RED END
\begin{widetext}
\begin{align}
\mathcal{V}^{\mathrm{ab}} (\omega) 
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha) + 
2\mu^{\mathrm{abxy}}(\omega)
E^{2}(\omega)\cos(\alpha)\sin(\alpha)}
{\xi^{\mathrm{xx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha)},
\nonumber \\
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)\sin^{2}(\alpha) + 
\mu^{\mathrm{abxy}}(\omega)\sin(2\alpha)}
{\xi^{\mathrm{xx}}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)}.
\label{eq:vab}
\end{align}
\end{widetext}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Layer by layer %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\color{red}
\subsection{Layer-by-layer analysis.}\label{sec:theory-layer}

@@

} % COLOR RED END

@@

{\color{red}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% Res: mu & V^{ab} comparison %%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{plots/vab-str-comp}
    \caption{Comparison of most intense responses for
    $\mathcal{V}^{\mathrm{ab}}$ for \emph{alt}, \emph{up}, CdSe, and GaAs
    structures}
    \label{fig:vab-str-comp}
\end{figure}

In figure \ref{fig:vab-str-comp} we present a comparison of the most intense
responses resulting from evaluate the Eq. \eqref{eq:vab} for the \emph{alt} and
\emph{up} 2D structures vs. CdSe and GaAs bulk structures. As we can see from
this figure the most intense response corresponds to the \emph{up} structure
centered at 0.088\,eV corresponding to the terahertz radiation and reaching a
spin velocity of 87.16\,Km/s.
% 
In the other hand, for an energy range from 0.66\,eV to 3.0\,eV all the
four structures have contributions in the same order of magnitude. 
% 
Starting with the 2D structures we have that the \emph{up} structure has other
two peaks centered at 1.94\,eV and 1.97\,eV reaching spin velocities of
22.2\,Km/s and -29.7\,Km/s, respectively, and the \emph{alt} structure has two
peaks centered at 0.72\,eV and 0.91\,eV reaching spin velocities of -40.2\,Km/s
and -32.9\,Km/s, respectively.
% 
Then, for the bulk structures we have that the CdSe has only one intense
response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
GaAs structure has a large and almost planar zone where the response is hold
reaching the maximum for an incoming beam of energy of 2.31\,eV and reaching a
spin velocity of -21.6\,Km/s.
% 
In table \ref{tab:vab-str-comp} we present the comparison of this values for the 2D and bulk structures.
% 
\begin{table}[t]

\begin{tabular}{cccccc}
\hline
\multirow{2}{*}{Structure \quad} & 
Kind of \quad & 
Pol. &
Energy & 
\multicolumn{2}{c}{$\mathcal{V}^{\mathrm{ab}}(\omega)$}\\
\cline{5-6}
& system & Ang. & [eV] & $\mathrm{ab}$ \quad & [Km/s]\\
\hline
\emph{up}    & 2D   & 40    & 0.09  & $\mathrm{yz}$ &  87.16    \\
             &      &       & 1.94  & $\mathrm{yz}$ &  22.22    \\
             &      &       & 1.97  & $\mathrm{yz}$ & -29.70    \\ \\
\emph{alt}   & 2D   & 145   & 0.72  & $\mathrm{yz}$ & -40.21    \\
             &      &       & 0.91  & $\mathrm{yz}$ & -32.89    \\ \\
 CdSe        & bulk & 90    & 0.91  & $\mathrm{zz}$ & -26.87    \\ \\
 GaAs        & bulk & 90    & 2.31  & $\mathrm{xx}$ & -21.62    \\
\hline
\end{tabular}
\caption{\color{red} Comparison of the reported maxima values of $\mathcal{V}^{\mathrm{ab}}$
for different structures and the corresponding polarization angle $\alpha$ and
energy values.}
\label{tab:vab-str-comp}
\end{table}
} % COLOR RED END
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%% Results: Fixing spin %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$ for \emph{up} structure 
    \label{fig:up-3d-vsx-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-svax-1}}
    \\
    \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$ for \emph{up} structure 
    \label{fig:up-3d-vsy-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-svay-1}}
    \\
    \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ for \emph{up} structure 
    \label{fig:up-3d-vsz-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-svaz-1}}

    \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$,
    $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$, and
    $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ responses for the \emph{up}
    structure.}
    \label{fig:up-3d-vsb-1}
\end{figure}

\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$ for \emph{up} structure 
    \label{fig:up-3d-vsx-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-svax-2}}
    \\
    \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$ for \emph{up} structure 
    \label{fig:up-3d-vsy-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-svay-2}}
    \\
    \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$ for \emph{up} structure 
    \label{fig:up-3d-vsy-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-svaz-2}}

    \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$,
    $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$, and
    $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ responses for the \emph{up}
    structure.}
    \label{fig:up-3d-vsb-1}
\end{figure}

\begin{figure}[t]
    \centering
    \subfigure[\ \label{fig:up-vaz-rag-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-1}}
    \\
    \subfigure[\ \label{fig:up-vaz-rag-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-2}}

    \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ response for the
    \emph{up} structure.}
    \label{fig:up-vaz-rag}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixing spin Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vsx}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-svax}}
    \\
    \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vsy}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-svay}}
    \\
    \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vsz}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-svaz}}

    \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$,
    $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$, and
    $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ responses for \emph{alt} structure. }
    \label{fig:alt-3d-vsb}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vaz-rag}
    \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ response for the
    \emph{alt} structure.}
    \label{fig:figure1}
\end{figure}

@@

% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V^{a}| 3D
% %% files: 
% %% magv.sm_0.03_xb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% magv.sm_0.03_yb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% up-3d-vab.gp
% %%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vvx-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{up} structure 
    \label{fig:up-3d-vvy-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
    structure. The maximum response zone is localized for an energy range from
    0.04\,eV to 0.12\,eV and for a polarization angle of the
    incoming beam from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-3d-vva-1}
\end{figure}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}
    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
    \emph{up} structure. Both maxima where obtained for a polarization
    angle $\alpha=40^{\circ}$. }
    \label{fig:up-vab-comp-rtp-1}
\end{figure}

For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
0.16\,eV where we found the most intense response for $\mathcal{V}^{\mathrm{x}}$
and $|\mathcal{V}^{\mathrm{y}}|$. In Fig. \ref{fig:up-3d-vva-1} we present the
$\mathcal{V}^{\mathrm{a}}$ spectra resulting from evaluate again Eq. 
\eqref{eq:vv-mag} using different polarization angles $\alpha$ in Eq.  
\eqref{eq:vab} but now for the C$_{16}$H$_{8}$-up structure. We can see that the
onset of the response is when the energy of the incoming light is the same of
the gap energy.
% 
From this picture we can see that for the zone between the energy range of
0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
$45^{\circ}$ is the zone where the maximum zone of response for both,
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ is hold.
% 
We found that the absolute maximum of the response is obtained when the
polarization angle is $\alpha=40^{\circ}$ and the energy of the incoming beam is
0.088\,eV.
%
In the top frames of  Figs. \ref{fig:up-vx-comp-rtp-1} and 
% 
\ref{fig:up-vy-comp-rtp-1} we present the results of
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ (left scale)
fixing the polarization angle to $\alpha=40^{\circ}$ for the \emph{up} structure
vs photon energy and the corresponding polar $\varphi$ and azimuthal $\theta$
angles (right scale). In the bottom frames of same figures we present the decomposition of
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ in the
corresponding $\mathcal{V}^{\mathrm{xx}}$, 
$\mathcal{V}^{\mathrm{xy}}$,
$\mathcal{V}^{\mathrm{xz}}$, and
$\mathcal{V}^{\mathrm{yx}}$, 
$\mathcal{V}^{\mathrm{yy}}$,
$\mathcal{V}^{\mathrm{yz}}$ 
components with $\alpha$ fixed to $40^{\circ}$. 
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vvx-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{up} structure 
    \label{fig:up-3d-vvy-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$
    response for C$_{16}$H$_{8}$-up structure. The local maxima responses zones
    are localized for an energy range from 1.95\,eV to 2.00\,eV and for
    polarization angles of the incoming beam from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-3d-vva-2}
\end{figure}

@@

1.80\,eV to 2.10\,eV presented in Fig. \ref{fig:up-3d-vva-2} where two local maxima

@@

\textbf{Alt structure.}
% %%%%%%%%%%%%%%%%%
% %% Description of ALT |V^{a}| 3D
% %% files: 
% %% magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
% %% magv.sm_0.03_yb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
% %% alt-3d-vab.gp
% %%%%%%%%%%%%%%%%%
\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vvx}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vxb}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vvy}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vyb}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$
    responses for C$_{16}$H$_{8}$-alt structure. The maxima responses zones are
    localized for an energy range from 0.90\,eV to 0.93\,eV and for polarization
    angles of the incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
    \label{fig:alt-3d-vva}
\end{figure}

@@

\ref{fig:alt-3d-vva} we present the $|\mathcal{V}^{\mathrm{a}}|$ spectra resulting 
